---
title: "GRAD 695 Executive Class"
author: Qiulin Peng
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
income <- read.csv("~/income.csv", header = TRUE)
```

## Introduction

We are using the Income dataset and try to answer the research question, so we first explore the dataset to have dataset overview.
```{r}
nrow(income)
summary(income)
```

We see that we have 535 records and 8 variables. 

An interesting question will be: Are there any difference in income of people from different industries?

## Exploratory Data Analysis

### Correlation between Numeric Variables
```{r}
numeric_var <- c("All_workers","All_weekly","M_workers","M_weekly","F_workers","F_weekly")
numeric_df <- income[numeric_var]
cor(numeric_df)
```

Weekly income data have more than half are missing value, so we focus on the worker income variables. It shows that All_worker is highly correlated (>0.83) with M_workers and F_workers, and it suggests that if we include both All_workers and M_workers/F_workers in the model, there will be multilinearity issue. We also see that correlation coefficient between M_worker and F_workers is about 0.39, and it does not have high correlation. Therefore, we will include M_workers and F_workers or All_workers only as numeric variables.

### ANOVA Test of Industry Income
```{r}
boxplot(income$All_workers~income$Industry, main='Boxplot of Income Difference Among Industry', xlab='Industry', ylab='Average Income')
```

The boxplot shows that the mean income varies among industry. ANOVA test results show that p-value < 0.05, therefore we reject the null hypothesis that the mean incomes are the same among industries, and can conclude that the there are significant differences in mean income among different industries.

```{r}
summary(aov(All_workers~Industry, data = income))
```

### Gender Income Difference
```{r}
t.test(income$M_workers,income$F_workers)
```

The t-test results show that, the mean income for males worker is $113, and mean income for female worker is $90. However the p-value = 0.09 > 0.05, so we cannot reject the null hypothesis, and it means we can conclude that there's no significant difference of mean income between gender.

## Regression Analysis

```{r}
```

## Conclusion